Sketch Recognition and Understanding

### 2009-08-17 trunk/draft/Results.tex
after most changes

 \begin{table*}
	\centering
	%\small
%	\scalebox{0.7}{
		%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
	\scalebox{0.7}{
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
		Categorie / classified as ==$>$	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout	&Number of sample per class	&TP count	&FP count	&Fn	&Precision	&Recall ( TP rate )\\
ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0	&152	&150	&27	&2	&0.84745762711864	&0.98684210526316\\
heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0	&152	&130	&20	&22	&0.86666666666667	&0.85526315789474\\
trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0	&150	&147	&50	&3	&0.74619289340102	&0.98\\
pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0	&152	&139	&9	&13	&0.93918918918919	&0.91447368421053\\
arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1	&151	&125	&25	&26	&0.83333333333333	&0.82781456953642\\
hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0	&151	&135	&2	&16	&0.98540145985401	&0.89403973509934\\
square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0	&151	&138	&1	&13	&0.99280575539568	&0.91390728476821\\
triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0	&151	&148	&20	&3	&0.88095238095238	&0.98013245033113\\
cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0	&153	&146	&6	&7	&0.96052631578947	&0.95424836601307\\
cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0	&152	&147	&2	&5	&0.98657718120805	&0.96710526315789\\
parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0	&150	&107	&4	&43	&0.96396396396396	&0.71333333333333\\
moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5	&153	&125	&21	&28	&0.85616438356164	&0.81699346405229\\
callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145	&151	&145	&0	&6	&1	&0.96026490066225\\
Total 	&152	&152	&150	&152	&151	&151	&151	&151	&153	&152	&150	&153	&151	&	&	&	&	&	&\\ 
% Categories 	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout\\ \hline 
%ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0\\  \hline 
%heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0\\  \hline 
%trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0\\  \hline 
%pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0\\   \hline 
%arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1\\   \hline 
%hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0\\  \hline 
%square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0\\   \hline 
%triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0\\  \hline 
%cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0\\   \hline 
%cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0\\  \hline 
%parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0\\  \hline 
%moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5\\   \hline 
%callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145\\  \hline 
 		\end{tabular}
			}
 		%\end{tabular}
 	%}
	\caption{Confusion Matrix of HS-DB}
	\label{tab:ConfusionMatrix}
	%\end{minipage}
\end{table*}

>>>>

 \begin{table*}
	\centering
	%\small
%	\scalebox{0.7}{
		%	\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}\hline 
	\scalebox{0.5}{
		\begin{tabular}{|p{2cm}|c|c|c|c|c|c|c|c|c|c|c|c|c||p{2cm}|c|c|c|c|p{2cm}|}\hline 
		Categorie / classified as ==$>$	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout	&Number of samples per class	&TP count	&FP count	&Fn	&Precision	&Recall ( TP rate )\\ \hline 
ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0	&152	&150	&27	&2	&0.8474	&0.9868\\ \hline 
heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0	&152	&130	&20	&22	&0.86666	&0.8552\\ \hline 
trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0	&150	&147	&50	&3	&0.7461	&0.98\\ \hline 
pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0	&152	&139	&9	&13	&0.9391	&0.91447\\ \hline 
arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1	&151	&125	&25	&26	&0.83333	&0.82781\\ \hline 
hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0	&151	&135	&2	&16	&0.9854	&0.89403\\ \hline 
square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0	&151	&138	&1	&13	&0.9928	&0.91390\\ \hline 
triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0	&151	&148	&20	&3	&0.88095	&0.98013\\ \hline 
cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0	&153	&146	&6	&7	&0.96052	&0.95424\\ \hline  
cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0	&152	&147	&2	&5	&0.98657	&0.967105\\ \hline 
parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0	&150	&107	&4	&43	&0.963	&0.71333\\  \hline 
moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5	&153	&125	&21	&28	&0.8561	&0.8169\\ \hline  
callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145	&151	&145	&0	&6	&1	&0.9602\\  \hline  
% Categories 	&ellipse	&heart	&trapezoid	&pentagon	&arch	&hexagon	&square	&triangle	&cube	&cylinder	&parallelogram	&moon	&callout\\ \hline 
%ellipse	&150	&20	&0	&0	&0	&5	&1	&0	&0	&0	&0	&1	&0\\  \hline 
%heart	&2	&130	&0	&1	&10	&1	&1	&0	&0	&0	&1	&4	&0\\  \hline 
%trapezoid	&0	&1	&147	&5	&1	&0	&1	&3	&2	&0	&37	&0	&0\\  \hline 
%pentagon	&0	&0	&1	&139	&0	&7	&0	&0	&0	&0	&1	&0	&0\\   \hline 
%arch	&0	&0	&1	&1	&125	&0	&4	&0	&3	&0	&0	&15	&1\\   \hline 
%hexagon	&0	&0	&0	&2	&0	&135	&0	&0	&0	&0	&0	&0	&0\\  \hline 
%square	&0	&0	&0	&0	&0	&0	&138	&0	&0	&0	&0	&1	&0\\   \hline 
%triangle	&0	&0	&1	&2	&5	&0	&1	&148	&0	&0	&4	&7	&0\\  \hline 
%cube	&0	&0	&0	&1	&0	&0	&0	&0	&146	&5	&0	&0	&0\\   \hline 
%cylinder	&0	&0	&0	&1	&0	&1	&0	&0	&0	&147	&0	&0	&0\\  \hline 
%parallelogram	&0	&0	&0	&0	&0	&0	&2	&0	&2	&0	&107	&0	&0\\  \hline 
%moon	&0	&1	&0	&0	&10	&2	&3	&0	&0	&0	&0	&125	&5\\   \hline 
%callout	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&0	&145\\  \hline 
 		\end{tabular}
			}
 		%\end{tabular}
 	%}
	\caption{Confusion Matrix of HS-DB}
	\label{tab:ConfusionMatrix}
	%\end{minipage}
\end{table*}
